---
title: "WY BILT Exit Survey"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    css: style.css
    logo: MR_Stacked_wht.png
    orientation: rows
    vertical_layout: scroll
    navbar:
    - icon: fa-twitter
      href: https://twitter.com/MarzanoResearch
      align: right
    - icon: fa-linkedin
      href: https://www.linkedin.com/company/marzano-research/
      align: right
    - icon: fa-facebook
      href: https://www.facebook.com/MarzanoResearch/
      align: right
    - icon: fa-envelope
      href: https://www.marzanoresearch.com/contact
      align: right
    - title: Marzano Research
      href: https://www.marzanoresearch.com/
      align: right
    theme:
      version: 4
      bg: '#ffffff'
      fg: '#101010'
      navbar-bg: '#495E82'
resource_files:
- data/wy_bilt.sav
- data/wy_bilt_district_list.xlsx
---

<script>
$('.navbar-logo').wrap('<a href="https://www.marzanoresearch.com/" target=_blank>');
</script>


<style>
.nav-tabs-custom .nav-tabs li.active a {
  color: black;
}

.nav-tabs-custom .nav-tabs li:not(.active) a {
  color: black;
}

</style>



```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
```

```{r, include=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(rio)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(glue)
library(fs)
library(rstatix)
library(ggpubr)
library(writexl)
library(remotes)
library(profvis)

theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(colour = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )

```

```{r, include=FALSE}
wy_bilt <- import(here("data", "wy_bilt.sav"),
               setclass = "tbl_df") %>% 
  characterize() %>% 
  janitor::clean_names() %>% 
  mutate(response_id = as.factor(response_id))

wy_bilt[sapply(wy_bilt, is.character)] <- lapply(wy_bilt[sapply(wy_bilt, is.character)],
                                                 as.factor)

str(wy_bilt)

district_list <- import(here("data", "wy_bilt_district_list.xlsx"),
                        setclass = "tbl_df")
```


# Demographics {data-icon="fa-id-card"}


Row {.tabset}
-----------------------------------------------------------------------

### Position/Role

```{r, include=FALSE}
names(wy_bilt)

wy_demo <- wy_bilt %>% 
  select(survey_number, response_id, q_8) %>% 
  group_by(q_8) %>% 
  count()

demo_tbl <- wy_demo %>% 
  reactable(
    columns = list(
      q_8 = colDef(name = "Position/Role",
                   align = "center"),
      n = colDef(name = "Total",
                 align = "center")),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
demo_tbl
```


### District 

```{r, include=FALSE}
wy_district <- wy_bilt %>% 
  select(survey_number, response_id, q_9)

wy_district$q_9 <- factor(wy_district$q_9, levels = c("Converse County School District 1",
                                                      "Fremont County School District 24",
                                                      "Goshen County School District 1",
                                                      "Laramie County School District 2",
                                                      "Lincoln County School District 1",
                                                      "Niobrara County School District 1",
                                                      "Park County School District 6",
                                                      "Platte County School District 2",
                                                      "Sweetwater County School District 1",
                                                      "Uinta County School District 6"))


wy_district_count <- wy_district %>% 
  group_by(q_9) %>% 
  count()

dist_tbl <- wy_district_count %>% 
  reactable(
    columns = list(
      q_9 = colDef(name = "School District",
                   align = "center"),
      n = colDef(name = "Total",
                 align = "center")),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )
```

```{r, include=TRUE}
dist_tbl
```


### Grades Worked With 

```{r, include=FALSE}

wy_grade <- wy_bilt %>% 
  select(survey_number, response_id, 27:42) %>% 
  group_by() 

wy_grade_long <- wy_grade %>% 
  pivot_longer(
    cols = c(3:18),
    names_to = "grade",
    names_prefix = "q_10_",
    values_to = "response"
  )

wy_grade_count <- wy_grade_long %>% 
  group_by(grade) %>% 
  count(response) %>% 
  filter(response == "Yes")

str(wy_grade_count)

wy_grade_count$grade <- factor(wy_grade_count$grade, levels = c("preK",
                                                                "K",
                                                                "g1",
                                                                "g2",
                                                                "g3",
                                                                "g4",
                                                                "g5",
                                                                "g6",
                                                                "g7",
                                                                "g8",
                                                                "g9",
                                                                "g10",
                                                                "g11",
                                                                "g12",
                                                                "other"))

levels(wy_grade_count$grade) <- c("PreK",
                                  "K",
                                  "1st",
                                  "2nd",
                                  "3rd",
                                  "4th",
                                  "5th",
                                  "6th",
                                  "7th",
                                  "8th",
                                  "9th",
                                  "10th",
                                  "11th",
                                  "12th",
                                  "Other")

wy_grade_count$grade <- factor(wy_grade_count$grade, levels = c("PreK",
                                  "K",
                                  "1st",
                                  "2nd",
                                  "3rd",
                                  "4th",
                                  "5th",
                                  "6th",
                                  "7th",
                                  "8th",
                                  "9th",
                                  "10th",
                                  "11th",
                                  "12th",
                                  "Other"))

grade_tbl <- wy_grade_count %>% 
  select(grade, n) %>% 
  reactable(
    columns = list(
      grade = colDef(name = "Grade",
                   align = "center"),
      n = colDef(name = "Total",
                 align = "center")),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )
```

```{r, include=TRUE}
grade_tbl
```

Row {.tabset}
-----------------------------------------------------------------------

### Training Attended 

```{r, include=FALSE}
names(wy_bilt)

training_attended <- wy_bilt %>% 
  select(survey_number, response_id, training_type) %>% 
  group_by(training_type) %>% 
  count()

attend_tbl <- training_attended %>% 
  reactable(
    columns = list(
    training_type = colDef(name = "Training",
                   align = "center"),
      n = colDef(name = "Total",
                 align = "center")),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
```

```{r, include=TRUE}
attend_tbl
```


### Training Date

```{r, include=FALSE}
train_date <- wy_bilt %>% 
  select(survey_number, response_id, training_date, training_type) %>% 
  group_by(training_date, training_type) %>% 
  count()

train_date_tbl <- train_date %>% 
  reactable(
    columns = list(
      training_date = colDef(name = "Date",
                             align = "center"),
      training_type = colDef(name = "Training",
                             align = "center"),
      n = colDef(name = "Total",
                 align = "center")),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE)
```


```{r, include=TRUE}
train_date_tbl
```

# Survey Feedback {data-icon="fa-chart-bar"}

Sidebar {.sidebar}
------------

Survey responses on this tab correspond to the following prompt: As a result of the WY BILT training/technical assistance...

```{r, include=FALSE}
# question_3 <- wy_bilt %>% 
#   pivot_longer(
#     cols = c(11:17),
#     names_to = "question_3_prompts",
#     values_to = "response"
#   ) 
# 
# question_3 <- question_3 %>% 
#   mutate(question_3_prompts = recode(question_3_prompts, 
#                             `q_3_1` = "I have increased knowledge of how to address literacy issues",
#                             `q_3_2` = "I have an increased awareness of resources to address literacy issues",
#                             `q_3_3` = "I am better able to use resources to address literacy issues",
#                             `q_3_4` = "I have an increased capacity to provide high-quality literacy support for all students",
#                             `q_3_5` = "I intend to change educational practices related to the training",
#                             `q_3_6` = "I intend to change classroom or school policies related to the training",
#                             `q_3_7` = "Overall, I found this event useful"))

```


```{r, include=TRUE}
selectInput("training1",
            "Training:",
            choices = levels(wy_bilt$training_type))
```

```{r, include=TRUE}
# selectInput("prompts",
#             "Select Prompt:",
#             choices = levels(question_3$question_3_prompts))
```


```{r, include=FALSE}
q_3_df <- function(df, a, b, c, d, e) {
  df %>% 
    select({{a}}, {{b}}, {{c}}, {{d}}, {{e}}) %>% 
    group_by({{c}}, {{d}}, {{e}}) %>% 
    count({{e}}) 
}

q_3_1_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_3_1) %>% 
  rename("response" = q_3_1)


q_3_sv_resp1 <- c("Strongly Disagree",
                  "Disagree",
                  "Agree",
                  "Strongly Agree",
                  "Not applicable because it was not covered in the training")

q_3_sv_resp2 <- c("Not applicable because it\n was not covered in the training",
                  "Strongly Agree",
                  "Agree",
                  "Disagree",
                  "Strongly Disagree")

```

```{r, include=FALSE}
survey_plot_q3 <- function(df) {
  renderPlotly({
    df %>% 
      filter(training_type %in% input$training1) %>% 
      ggplot(aes(response, n)) +
      geom_col(fill = "#495E82") +
      scale_x_discrete(limits = q_3_sv_resp2) +
      scale_y_continuous(limits = c(0, 15),
                        breaks = c(0, 5, 10, 15)) +
      coord_flip() +
      labs(x = "",
           y = "Total Number of Responses")
  })
}

```


```{r, include=FALSE}
smry_tbl <- function(df) {
  df %>% 
    filter(training_type %in% input$training1) %>% 
    reactable(
      defaultColDef = colDef(align = "center"),
      columns = list(
        training_date = colDef(name = "Date"),
        training_type = colDef(name = "Training"),
        response = colDef(name = "Response"),
        n = colDef(name = "Total")),
        striped = TRUE,
        outlined = TRUE,
        compact = TRUE,
        highlight = TRUE,
        bordered = TRUE,
        searchable = TRUE)
}
```

Row {.tabset}
-----------------------------------------------------------------------

### I have **increased knowledge** of how to address literacy issues. 

```{r, include=TRUE}
survey_plot_q3(q_3_1_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl(q_3_1_res))
```


Row {.tabset}
-----------------------------------------------------------------------

### I have an **increased awareness** of resources to address literacy issues.

```{r, include=FALSE}
q_3_2_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_3_2) %>% 
  rename("response" = q_3_2)
```


```{r, include=TRUE}
survey_plot_q3(q_3_2_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl(q_3_2_res))
```

Row {.tabset}
-----------------------------------------------------------------------

### I am better able to **use resources** to address literacy issues.

```{r, include=FALSE}
q_3_3_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_3_3) %>% 
  rename("response" = q_3_3)
```


```{r, include=TRUE}
survey_plot_q3(q_3_3_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl(q_3_3_res))
```

Row {.tabset}
-----------------------------------------------------------------------

### I have an **increased capacity** to provide high-quality literacy support for all students.

```{r, include=FALSE}
q_3_4_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_3_4) %>% 
  rename("response" = q_3_4)
```


```{r, include=TRUE}
survey_plot_q3(q_3_4_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl(q_3_4_res))
```

Row {.tabset}
-----------------------------------------------------------------------

### I intend to **change educational practices** related to the training. 

```{r, include=FALSE}
q_3_5_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_3_5) %>% 
  rename("response" = q_3_5)
```


```{r, include=TRUE}
survey_plot_q3(q_3_5_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl(q_3_5_res))
```

Row {.tabset}
-----------------------------------------------------------------------

### I intend to **change classroom or school policies** related to the training. 

```{r, include=FALSE}
q_3_6_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_3_6) %>% 
  rename("response" = q_3_6)
```


```{r, include=TRUE}
survey_plot_q3(q_3_6_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl(q_3_6_res))
```

Row {.tabset}
-----------------------------------------------------------------------

### Overall, I found this event useful.

```{r, include=FALSE}
q_3_7_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_3_7) %>% 
  rename("response" = q_3_7)
```


```{r, include=TRUE}
survey_plot_q3(q_3_7_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl(q_3_7_res))
```

# Survey Feedback {data-icon="fa-chart-bar"}

Sidebar {.sidebar}
------------

Survey responses on this tab correspond to the following prompt: Please indicate your level of agreement with the following statements

```{r, include=TRUE}
selectInput("training2",
            "Training:",
            choices = levels(wy_bilt$training_type))
```

```{r, include=FALSE}
q_4_1_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_4_1) %>% 
  rename("response" = q_4_1)

q_4_sv_resp1 <- c("Strongly Disagree",
                  "Disagree",
                  "Agree",
                  "Strongly Agree")

q_4_sv_resp2 <- c("Strongly Agree",
                  "Agree",
                  "Disagree",
                  "Strongly Disagree")

```


```{r, include=FALSE}
survey_plot_q4 <- function(df) {
  renderPlotly({
    df %>% 
      filter(training_type %in% input$training2) %>% 
      ggplot(aes(response, n)) +
      geom_col(fill = "#495E82") +
      scale_x_discrete(limits = q_4_sv_resp2) +
      scale_y_continuous(limits = c(0, 15),
                        breaks = c(0, 5, 10, 15)) +
      coord_flip() +
      labs(x = "",
           y = "Total Number of Responses")
  })
}

```

```{r, include=FALSE}
smry_tbl2 <- function(df) {
  df %>% 
    filter(training_type %in% input$training2) %>% 
    reactable(
      defaultColDef = colDef(align = "center"),
      columns = list(
        training_date = colDef(name = "Date"),
        training_type = colDef(name = "Training"),
        response = colDef(name = "Response"),
        n = colDef(name = "Total")),
        striped = TRUE,
        outlined = TRUE,
        compact = TRUE,
        highlight = TRUE,
        bordered = TRUE,
        searchable = TRUE)
}
```


Row {.tabset}
-----------------------------------------------------------------------

### The goal or purpose of the training/activity was clearly stated at or before the beginning of the event. 

```{r, include=TRUE}
survey_plot_q4(q_4_1_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl2(q_4_1_res))
```

Row {.tabset}
-----------------------------------------------------------------------

### The structure of the training/activity was appropriate for meeting the stated goals.

```{r, include=FALSE}
q_4_2_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_4_2) %>% 
  rename("response" = q_4_2)
```

```{r, include=TRUE}
survey_plot_q4(q_4_2_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl2(q_4_2_res))
```

Row {.tabset}
-----------------------------------------------------------------------

### The training/activity was relevant to a literacy issue or problem currently facing my school/district

```{r, include=FALSE}
q_4_3_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_4_3) %>% 
  rename("response" = q_4_3)
```

```{r, include=TRUE}
survey_plot_q4(q_4_3_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl2(q_4_3_res))
```

Row {.tabset}
-----------------------------------------------------------------------

### The presenter/trainer was knowledgeable or experienced with the topic addressed. 

```{r, include=FALSE}
q_4_4_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_4_4) %>% 
  rename("response" = q_4_4)
```

```{r, include=TRUE}
survey_plot_q4(q_4_4_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl2(q_4_4_res))
```

Row {.tabset}
-----------------------------------------------------------------------

### I am satisfied with the overall quality of this training/activity. 

```{r, include=FALSE}
q_4_5_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_4_5) %>% 
  rename("response" = q_4_5)
```

```{r, include=TRUE}
survey_plot_q4(q_4_5_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl2(q_4_5_res))
```

Row {.tabset}
-----------------------------------------------------------------------

### I would recommend the training to other potential participants. 

```{r, include=FALSE}
q_4_6_res <- q_3_df(wy_bilt,
                    survey_number, 
                    response_id, 
                    training_date,
                    training_type,
                    q_4_6) %>% 
  rename("response" = q_4_6)
```

```{r, include=TRUE}
survey_plot_q4(q_4_6_res)
```

### Summary 

```{r, include=TRUE}
renderReactable(smry_tbl2(q_4_6_res))
```

# Additional Comments {data-icon="fa-comment"}

Sidebar {.sidebar}
------------

The data tables on this page detail descriptive responses for each individual who completed the survey: 

  1. What useful information and/or practical techniques did you learn as a result of this training/activity? 
  2. What about the content of this training/activity could be changed to improve it?
  3. As a result of this training/activity, what steps do you plan to take? What changes do you plan to implement? 

```{r, include=FALSE}
q_5_7_df <- function(df, a, b) {
  df %>% 
    select({{a}}, {{b}}) 
}

```


Row 
-----------------------------------------------------------------------

### What useful information and/or practical techniques did you learn as a result of this training activity?

```{r, include=FALSE}
q_5_res <- q_5_7_df(wy_bilt, survey_number, q_5)

q_5_tbl <- q_5_res %>% 
    reactable(
     columns = list(
     survey_number = colDef(name = "Respondent",
                   align = "center"),
      q_5 = colDef(name = "Total",
                 align = "center")),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )
```

```{r, include=TRUE}
q_5_tbl
```


Row 
-----------------------------------------------------------------------

### What about the content of this training/activity could be changed to improve it?

```{r, include=FALSE}
q_6_res <- q_5_7_df(wy_bilt, survey_number, q_6)

q_6_tbl <- q_6_res %>% 
    reactable(
     columns = list(
     survey_number = colDef(name = "Respondent",
                   align = "center"),
      q_6 = colDef(name = "Total",
                 align = "center")),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )
```

```{r, include=TRUE}
q_6_tbl
```


Row 
-----------------------------------------------------------------------

### As a result of this training/activity, what steps do you plan to take? What changes do you plan to implement? 

```{r, include=FALSE}
q_7_res <- q_5_7_df(wy_bilt, survey_number, q_7)

q_7_tbl <- q_7_res %>% 
    reactable(
     columns = list(
     survey_number = colDef(name = "Respondent",
                   align = "center"),
      q_7 = colDef(name = "Total",
                 align = "center")),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )
```

```{r, include=TRUE}
q_7_tbl
```